\documentclass[a4paper,10pt]{article}

\usepackage{parskip} 
\usepackage{fontspec}
\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=0.12in, bottom=0.12in]{geometry}
\usepackage{tabularx}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{2pt}

\usepackage[unicode, colorlinks]{hyperref}
\hypersetup{
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}

\usepackage{fontawesome5}
\setmainfont{Arial}

\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

\begin{document}
\pagestyle{empty}

% Header
\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{1C033C} \Huge{Vansh Khatri} \\[1pt]
\textcolor[HTML]{371e77}{{\faEnvelope\ khatrivansh43@gmail.com}} $|$
\textcolor[HTML]{371e77}{{\faMobile\ 7300788546}} \\[1pt]
\textcolor[HTML]{371e77}{\href{https://www.linkedin.com/in/vansh-khatri-3589b1282/}{\raisebox{-0.05\height}{\faLinkedin} Linkedin}}
$|$
\textcolor[HTML]{371e77}{\href{https://scasys.in}{\raisebox{-0.05\height}{\faBuilding} Scasys}}
\end{tabularx}

% Professional Summary
\section{Summary}
\textcolor[HTML]{1C033C}{
Founder, engineer, and operator focused on \textbf{scaling businesses} through technology, strategy, and people — with core expertise in \textbf{full-stack software development} and \textbf{AWS cloud optimisation}. Hands-on experience building and shipping \textbf{SaaS}, \textbf{D2C e-commerce}, and \textbf{immersive experience platforms}, while leading \textbf{corporate operations}, \textbf{hiring}, and \textbf{high-performance teams} from zero. Real-world track record running a \textbf{tech services company}, an \textbf{EMR product}, and \textbf{philanthropic initiatives} — with a long-term mindset of building ventures that are both scalable and sustainable.
}

% Education
\section{Education}
\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\color[HTML]{1C033C} \textbf{Class 12 (CBSE)} & \hfill & \color[HTML]{371e77} 2023 \\
\color[HTML]{371e77} Completed Higher Secondary Education & \hfill & \color[HTML]{4B28A4} \textit{\textbf{91.4\%}} \\
\end{tabularx}
\vspace{-2pt}
\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\color[HTML]{1C033C} \textbf{Malaviya National Institute of Technology, Jaipur} & \hfill & \color[HTML]{371e77} Aug 2023 -- Jun 2027 \\
\color[HTML]{371e77} B.Tech. in Computer Science and Engineering & \hfill & \color[HTML]{4B28A4} \textit{\textbf{CGPA: 7.9/10}} \\
\end{tabularx}

% Experience
\section{Experience}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\textbf{Software Engineering Intern} & \hfill & \textcolor[HTML]{371e77}{May 2025 -- July 2025} \\
\textcolor[HTML]{371e77}{\textbf{Air Force Station, Jaipur, Indian Air Force}} & & \\
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em, itemsep=0pt, topsep=0pt]
\item Developed \textbf{NetraX}, a health \& reliability monitoring system for cellular networks across multiple Air Force stations.
\item Automated diagnostics and real-time risk alerts, cutting daily inspection time by \textbf{60\%} and network failures by \textbf{40\%}.
\item Built a secure microservices backend and officer dashboard with role-based access control.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\textbf{Chief of Technical Staff} & \hfill & \textcolor[HTML]{371e77}{Dec 2024 -- May 2025} \\
\textcolor[HTML]{371e77}{\textbf{Re-verse Green Clothing Pvt Ltd}} & & \\
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em, itemsep=0pt, topsep=0pt]
\item Built initial technology infrastructure from scratch; led all technical decisions and end-to-end platform architecture.
\item Managed hiring of technical and management staff; overseeing team building across engineering and operations functions.
\item Deployed multiple tech platforms optimising manufacturing facility operations, increasing efficiency by \textbf{35\%} and throughput speed by \textbf{40\%}.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\textbf{Founder \& CEO} & \hfill & \textcolor[HTML]{371e77}{May 2025 -- Present} \\
\textcolor[HTML]{371e77}{\textbf{SCASYS Technologies Pvt Ltd (Scalable Systems)}} & & \\
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em, itemsep=0pt, topsep=0pt]
\item Founded as a tech services \& consulting company building and managing full operational technology for startups and NGOs; clients include \textbf{Sahayta NGO}, Jaipur.
\item Led client dealings, technical decision-making, team leadership, and full financial management with a sustainable and profitable mindset.
\item Launched \textbf{DOCSYS EMR} (\href{https://docsys.in}{docsys.in}), a cloud-native EMR product for clinics; went live \textbf{Nov 2025}, halted \textbf{Feb 2026} due to funding constraints; currently in acquisition talks.
\item Pivoted back to tech services \& consulting; managing infrastructure and product development across multiple active clients.
\end{itemize}

% Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Re-verse Platform Suite} & \textcolor[HTML]{371e77}{2024 -- Present} \\
\multicolumn{2}{@{}X@{}}{\textcolor[HTML]{371e77}{\textbf{Re-verse Green Clothing Pvt. Ltd.} \quad \href{https://re-verse.in}{\textcolor[HTML]{4B28A4}{\faExternalLink* re-verse.in}}}}
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em, itemsep=0pt, topsep=0pt]
\item Designed a multi-vendor e-commerce suite with real-time order, logistics, and communication workflows via WebSockets and external APIs.
\item \textbf{Stack:} Next.js, Express.js, MongoDB, Socket.IO, Razorpay, iThink Logistics API, WhatsApp API.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{ResumeGenie.live -- AI Resume Builder} & \textcolor[HTML]{371e77}{Apr 2025} \\
\multicolumn{2}{@{}X@{}}{\textcolor[HTML]{371e77}{\textbf{Placement \& Training Cell, MNIT Jaipur} \quad \href{https://resumegenie.live}{\textcolor[HTML]{4B28A4}{\faExternalLink* resumegenie.live}}}}
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em, itemsep=0pt, topsep=0pt]
\item Awarded \textbf{TechXcel 2025}; actively used by MNIT Jaipur's Training \& Placement Cell to help students build consistent, recruiter-ready resumes at scale.
\item Template-based AI generation, GitHub OAuth verification, automated PDF export; \textbf{Stack:} React.js, Node.js, Express.js, MongoDB, AI/ML.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Weinix -- Immersive 3D D2C Experience Platform} & \textcolor[HTML]{371e77}{2025 -- Present} \\
\multicolumn{2}{@{}X@{}}{\textcolor[HTML]{371e77}{\textbf{Sustainable Brand (Recycled Architectural Bricks)} \quad \href{https://weinix.com}{\textcolor[HTML]{4B28A4}{\faExternalLink* weinix.com}}}}
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em, itemsep=0pt, topsep=0pt]
\item Built and deployed a D2C website featuring a real-time \textbf{3D architectural model viewer} allowing customers to visualise recycled brick applications, increasing trust and conversion rate.
\item \textbf{Stack:} Next.js, Three.js / WebGL, Node.js, MongoDB, AWS.
\end{itemize}

% Technical Skills
\section{Technical Skills}
\color[HTML]{1C033C}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming:}    & C++, JavaScript, TypeScript, Python, SQL \\
\textbf{Frameworks:}     & Next.js, React.js, Node.js, Express.js, Django, TailwindCSS, Socket.IO \\
\textbf{Databases:}      & MongoDB, SQL \\
\textbf{Cloud / DevOps:} & AWS (EC2, EBS, RDS, ACM, Route53), Docker \\
\textbf{ML:}             & ML Pipelines, TensorFlow, PyTorch \\
\textbf{Tools:}          & Git, GitHub, VS Code, Jupyter, LaTeX, Postman \\
\end{tabularx}

% Leadership and Activities
\section{Leadership and Activities}
\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\textbf{Science and Technology Society, MNIT Jaipur} & & \textcolor[HTML]{371e77}{Sep 2024 -- Present} \\
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em, itemsep=0pt, topsep=0pt]
\item \textbf{General Secretary} \textcolor[HTML]{371e77}{(May 2025 -- Present):} Leading Sphinx, Rajasthan's largest technomanagement fest.
\end{itemize}

\end{document}