\documentclass[a4paper,10pt]{article}

\usepackage{parskip} 
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=0.12in, bottom=0.12in]{geometry}
\usepackage{tabularx}
\usepackage{array}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{2pt}

\usepackage[unicode, colorlinks]{hyperref}
\hypersetup{
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}

\usepackage{etoolbox}
\robustify\href

\usepackage{fontawesome5}

\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

\begin{document}
\pagestyle{empty}

% ================= HEADER =================
\begin{tabularx}{\linewidth}{@{} C @{}}
{\color[HTML]{1C033C} \Huge Vansh Khatri} \\[2pt]

{\color[HTML]{371e77}
\faEnvelope\ khatrivansh43@gmail.com \quad \textbar{} \quad
\faMobile\ 7300788546
} \\[2pt]

{\color[HTML]{371e77}
\href{https://www.linkedin.com/in/vansh-khatri-3589b1282/}{\faLinkedin\ Linkedin}
\quad \textbar{} \quad
\href{https://scasys.in}{\faBuilding\ Scasys}
}
\end{tabularx}

% ================= SUMMARY =================
\section{Summary}
{\color[HTML]{1C033C}
Founder, engineer, and operator focused on \textbf{scaling businesses} through technology, strategy, and people — with core expertise in \textbf{full-stack software development} and \textbf{AWS cloud optimisation}. Hands-on experience building and shipping \textbf{SaaS}, \textbf{D2C e-commerce}, and \textbf{immersive experience platforms}, while leading \textbf{corporate operations}, \textbf{hiring}, and \textbf{high-performance teams} from zero.
}

% ================= EDUCATION =================
\section{Education}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
{\color[HTML]{1C033C} \textbf{Class 12 (CBSE)}} & \hfill & {\color[HTML]{371e77} 2023} \\
{\color[HTML]{371e77} Completed Higher Secondary Education} & \hfill & {\color[HTML]{4B28A4} \textit{\textbf{91.4\%}}} \\
\end{tabularx}

\vspace{-2pt}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
{\color[HTML]{1C033C} \textbf{Malaviya National Institute of Technology, Jaipur}} & \hfill & {\color[HTML]{371e77} Aug 2023 -- Jun 2027} \\
{\color[HTML]{371e77} B.Tech. in Computer Science and Engineering} & \hfill & {\color[HTML]{4B28A4} \textit{\textbf{CGPA: 7.9/10}}} \\
\end{tabularx}

% ================= EXPERIENCE =================
\section{Experience}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\textbf{Software Engineering Intern} & \hfill & {\color[HTML]{371e77} May 2025 -- July 2025} \\
{\color[HTML]{371e77} \textbf{Air Force Station, Jaipur, Indian Air Force}} & & \\
\end{tabularx}

\vspace{-6pt}
\begin{itemize}[nosep, leftmargin=1.5em]
\item Developed \textbf{NetraX}, a health \& reliability monitoring system.
\item Reduced inspection time by \textbf{60\%}.
\item Built secure microservices backend.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\textbf{Chief of Technical Staff} & \hfill & {\color[HTML]{371e77} Dec 2024 -- May 2025} \\
{\color[HTML]{371e77} \textbf{Re-verse Green Clothing Pvt Ltd}} & & \\
\end{tabularx}

\vspace{-6pt}
\begin{itemize}[nosep, leftmargin=1.5em]
\item Built infrastructure and led architecture.
\item Improved efficiency by \textbf{35\%}.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\textbf{Founder \& CEO} & \hfill & {\color[HTML]{371e77} May 2025 -- Present} \\
{\color[HTML]{371e77} \textbf{SCASYS Technologies Pvt Ltd}} & & \\
\end{tabularx}

\vspace{-6pt}
\begin{itemize}[nosep, leftmargin=1.5em]
\item Founded tech services company.
\item Built \textbf{DOCSYS EMR}, in acquisition talks.
\end{itemize}

% ================= PROJECTS =================
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Re-verse Platform Suite} & {\color[HTML]{371e77} 2024 -- Present} \\
\multicolumn{2}{@{}X@{}}{
{\color[HTML]{371e77}
\textbf{Re-verse Green Clothing Pvt. Ltd.} \quad
\href{https://re-verse.in}{re-verse.in}
}
}
\end{tabularx}

\vspace{-6pt}
\begin{itemize}[nosep, leftmargin=1.5em]
\item Built multi-vendor e-commerce system.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{ResumeGenie.live} & {\color[HTML]{371e77} Apr 2025} \\
\end{tabularx}

\vspace{-6pt}
\begin{itemize}[nosep, leftmargin=1.5em]
\item AI resume builder used by MNIT.
\end{itemize}

% ================= SKILLS =================
\section{Technical Skills}

\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming:} & C++, JavaScript, Python, SQL \\
\textbf{Frameworks:} & Next.js, React, Node.js \\
\textbf{Cloud:} & AWS, Docker \\
\textbf{Tools:} & Git, VS Code \\
\end{tabularx}

\end{document}