\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}



\namesection{Divyansh}{Saraswat}{ \urlstyle{same}
\href{mailto:2022uch1062@mnit.ac.in}{2022uch1062@mnit.ac.in} | 9509333025
}

\begin{minipage}[t]{0.33\textwidth}

\section{Education}

\subsection{MNIT Jaipur}
\descript{BTech in Chemical Engineering}
\location{Jaipur, India}
\location{ Cum. CGPA: 8.3 / 10.0 }
\sectionsep

\subsection{Senior Secondary}
\location{97.0\% | CBSE Board}
\sectionsep

\subsection{Higher Secondary}
\location{94.5\% | CBSE Board}
\sectionsep

\section{Skills}
\subsection{Programming}
C/C++ \textbullet{} Python \textbullet{} JavaScript \textbullet{} Golang \\
SQL \textbullet{} Git/GitHub \textbullet{} MongoDB \textbullet{} VectorDB \\
LLM Training \& Inferencing \textbullet{} Adobe Suite \\
\sectionsep

\section{Languages}
Hindi \textbullet{} English
\sectionsep

\section{Hobbies}
Design \textbullet{} Chess \textbullet{} Art \\
Reading Tech Blogs
\sectionsep





\section{Leadership}
\runsubsection{Tech Secretary, Science-Tech Society}
\descript{| MNIT Jaipur}
\location{2024- Current}
\sectionsep

\runsubsection{Technical Executive, Sphinx-2023}
\descript{| MNIT Jaipur}
\location{2023}
\sectionsep




\section{Links} 
GitHub:// \href{https://github.com/divyanshsaraswat}{\bf divyanshsaraswat} \\
LinkedIn:// \href{https://www.linkedin.com/in/divyanshsaraswat}{\bf divyanshsaraswat} \\
Twitter:// \href{https://twitter.com/imdivyanshmv}{\bf @imdivyanshmv} \\
Portfolio:// \href{https://portfolio-demo-topaz.vercel.app/}{\bf divyanshsaraswat.com} \\
Project:// \href{https://www.sphinx.org.in}{\bf sphinx.org.in}

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth}

\section{Objective}
I'm an undergraduate B.Tech student in Chemical Engineering at MNIT Jaipur, with a strong passion for Machine Learning, Web Development, Data Engineering, and AI-driven applications. I have a strong focus on problem-solving and continuously learning new tools and technologies.


\section{Experience}
\runsubsection{Re-Verse}
\descript{| Software Engineer Team Lead }
\location{Dec 2024 - Present | Ahmedabad, Gujarat}
\begin{itemize}

   \item Led end-to-end development of a sustainable fashion e-commerce platform, scaling to 900 users/month with team management, dashboard implementation, and designer onboarding.

\end{itemize}
\sectionsep

\section{Projects}

\runsubsection{SPHINX}
\descript{| Technical Secretary + Core Team Member }
\location{September 2024 – March 2025 | Jaipur,Rajasthan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built a 3D interactive event website using Next.js and Node.js; integrated MongoDB Atlas and deployed via AWS (EBS, S3).
\item Led backend scaling and optimization to handle 8,000+ users and 68,000+ page views; ensured 99.9\% uptime during peak traffic.
\item Implemented analytics and real-time monitoring with Vercel, optimizing asset delivery and boosting load times by 40\%.
\item Streamlined domain and DNS routing using AWS Route 53, enhancing global accessibility and response latency.
\end{tightemize}
\sectionsep

\runsubsection{Validate.AI — Chromium Extension for Misinformation Detection}
\descript{| Aug 2024 – Present}
\begin{tightemize}
\item Developed a Chromium browser extension that validates social media content using AI-powered claim verification and source cross-referencing.
\item Integrated LLM-based summarization and relationship mapping to provide users with contextual, trustworthy information.
\item Architected for scalability with future modules for image forgery detection and video deepfake identification.
\item Tech Stack: LLMs, NLP, Neural Networks, CNNs, Browser Extension APIs, Data Cleaning, Web Animations.
\end{tightemize}
\sectionsep

\runsubsection{DocuScan - Django OCR Web App}
\descript{| Apr 2025}
\begin{tightemize}
\item Built a full-stack OCR web app using Django, allowing users to upload or capture images to extract text with Tesseract OCR.
\item Implemented summarization (Sumy) and Hindi translation via Google Translate API; export to PDF/.txt supported.
\item Designed a modern, responsive UI with Tailwind CSS and integrated secure user authentication features.
\item Technologies: Django, Tesseract, NLP, Tailwind CSS, Google Translate API, Sumy, Image Processing.
\item \href{https://github.com/divyanshsaraswat/docuscan_django}{GitHub: divyanshsaraswat/docuscan\_django}
\end{tightemize}




\end{minipage}
\end{document}
