\documentclass[a4paper,10pt]{article}

\usepackage{parskip} 
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=0.12in, bottom=0.12in]{geometry}
\usepackage{tabularx}
\usepackage{array}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{2pt}

\usepackage[unicode, colorlinks]{hyperref}
\hypersetup{
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}

\usepackage{fontawesome5}

\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

\begin{document}
\pagestyle{empty}

% Header
\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{1C033C} \Huge{Vansh Khatri} \\[1pt]
\textcolor[HTML]{371e77}{{\faEnvelope\ khatrivansh43@gmail.com}} $|$
\textcolor[HTML]{371e77}{{\faMobile\ 7300788546}} \\[1pt]
\textcolor[HTML]{371e77}{\href{https://www.linkedin.com/in/vansh-khatri-3589b1282/}{\raisebox{-0.05\height}{\faLinkedin} Linkedin}}
$|$
\textcolor[HTML]{371e77}{\href{https://scasys.in}{\raisebox{-0.05\height}{\faBuilding} Scasys}}
\end{tabularx}

% Summary
\section{Summary}
\textcolor[HTML]{1C033C}{
Founder, engineer, and operator focused on \textbf{scaling businesses} through technology, strategy, and people — with core expertise in \textbf{full-stack software development} and \textbf{AWS cloud optimisation}. Hands-on experience building and shipping \textbf{SaaS}, \textbf{D2C e-commerce}, and \textbf{immersive experience platforms}, while leading \textbf{corporate operations}, \textbf{hiring}, and \textbf{high-performance teams} from zero. Real-world track record running a \textbf{tech services company}, an \textbf{EMR product}, and \textbf{philanthropic initiatives} — with a long-term mindset of building ventures that are both scalable and sustainable.
}

% Education
\section{Education}
\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\color[HTML]{1C033C} \textbf{Class 12 (CBSE)} & \hfill & \color[HTML]{371e77} 2023 \\
\color[HTML]{371e77} Completed Higher Secondary Education & \hfill & \color[HTML]{4B28A4} \textit{\textbf{91.4\%}} \\
\end{tabularx}
\vspace{-2pt}
\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\color[HTML]{1C033C} \textbf{Malaviya National Institute of Technology, Jaipur} & \hfill & \color[HTML]{371e77} Aug 2023 -- Jun 2027 \\
\color[HTML]{371e77} B.Tech. in Computer Science and Engineering & \hfill & \color[HTML]{4B28A4} \textit{\textbf{CGPA: 7.9/10}} \\
\end{tabularx}

% Experience
\section{Experience}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\textbf{Software Engineering Intern} & \hfill & \textcolor[HTML]{371e77}{May 2025 -- July 2025} \\
\textcolor[HTML]{371e77}{\textbf{Air Force Station, Jaipur, Indian Air Force}} & & \\
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em]
\item Developed \textbf{NetraX}, a health \& reliability monitoring system for cellular networks.
\item Automated diagnostics and real-time risk alerts, reducing inspection time by \textbf{60\%}.
\item Built secure microservices backend with role-based access control.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\textbf{Chief of Technical Staff} & \hfill & \textcolor[HTML]{371e77}{Dec 2024 -- May 2025} \\
\textcolor[HTML]{371e77}{\textbf{Re-verse Green Clothing Pvt Ltd}} & & \\
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em]
\item Built initial tech infrastructure and led platform architecture.
\item Managed hiring and team building across engineering and operations.
\item Improved efficiency by \textbf{35\%} and throughput by \textbf{40\%}.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
\textbf{Founder \& CEO} & \hfill & \textcolor[HTML]{371e77}{May 2025 -- Present} \\
\textcolor[HTML]{371e77}{\textbf{SCASYS Technologies Pvt Ltd}} & & \\
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em]
\item Founded a tech services company managing full-stack solutions for startups and NGOs.
\item Led product, infrastructure, hiring, and financial operations.
\item Built and launched \textbf{DOCSYS EMR}, now in acquisition talks.
\end{itemize}

% Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Re-verse Platform Suite} & \textcolor[HTML]{371e77}{2024 -- Present} \\
\multicolumn{2}{@{}X@{}}{\textcolor[HTML]{371e77}{\textbf{Re-verse Green Clothing Pvt. Ltd.} \quad \href{https://re-verse.in}{\textcolor[HTML]{4B28A4}{\faExternalLink* re-verse.in}}}}
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em]
\item Built multi-vendor e-commerce system with real-time workflows.
\item Stack: Next.js, Node.js, MongoDB, Socket.IO.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{ResumeGenie.live} & \textcolor[HTML]{371e77}{Apr 2025} \\
\end{tabularx}
\vspace{-8pt}
\begin{itemize}[nosep, leftmargin=1.5em]
\item AI resume builder used by MNIT placement cell.
\item Stack: React, Node.js, MongoDB, AI.
\end{itemize}

% Skills
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming:} & C++, JavaScript, Python, SQL \\
\textbf{Frameworks:} & Next.js, React, Node.js \\
\textbf{Cloud:} & AWS, Docker \\
\textbf{Tools:} & Git, VS Code, Postman \\
\end{tabularx}

\end{document}